---
title: "Exercises"
editor: visual
---

```{r}
pacman::p_load(Epi, 
               tidyverse)
```

## Exercises Using R

1.  Calculate $\sqrt{3^{2}+4^{2}}$

```{r}
sqrt(3^2 + 4^2)
```

2.  Find the probability above 4.3 in chi-squared distribution on 1 degree of freedom

```{r}
pchisq(4.3, 1)
```

### Functions

```{r}
p2o <- function(p) p/(1-p)
o2p <- function(o) o/(1+o)
```

```{r}
p2o(0.25)
```

```{r}
o2p(8)
```

```{r}
o2p(p2o(0.25))
```

Write a function

```{r}
p2o <- 
  function( p )
  {
    odds <- p / (1 - p)
    odds
  }
```

```{r}
p2o(2)
```

### Sequences

```{r}
seq(15, 85, by = 5)
```

```{r}
c(5, seq(20, 85, by = 5))
```

```{r}
3.7:8.1
```

### Vectors

1.  create a vector w with components 1, -1, 2, -2

```{r}
w <- c(1, -1, 2, -2)
```

2.  print the w vector

```{r}
w
```

3.  obtain a description of w

```{r}
str(w)
```

4.  create the vector w+1 and print it

```{r}
w+1
```

5.  create the vector (0, 1, 5, 10, 15...75) using `c()` and `seq()`

```{r}
c(0, 1, seq(5,75, by = 5))
```

6.  create a vector with 20 elements equally spaced between 7 and 23

```{r}
c(20, seq(7, 23))
```

### Births data

```{r}
data(births)
```

```{r}
?births
```

```{r}
str(births)
```

### Selects

```{r}
data(diet)
```

```{r}
births[1:10, "bweight"]
```

1.  print the data on the variable `gestwks` for subject 7 in births dataframe

```{r}
births[7, "gestwks"]
```

2.  print all the data for subject #7

    ```{r}
    births[7, ]
    ```

3.  Print all the data on the variable `gestwks`

    ```{r}
    births[, "gestwks"]
    ```

    ```{r}
    births$gestwks
    ```

## New variables

1.  Create a logical variable called `early` according to whether `gestwks` is less than 30 or not. Make a frequency table of early using `table`

```{r}
births %>% 
  mutate(early = gestwks < 30) %>% 
  with(table(.$early))
```

2.  Print the `id` numbers of women with `gestwks` less than 30 weeks

    ```{r}
    which(births$gestwks < 30)
    ```

```{r}
births %>% 
  filter(gestwks < 30) %>% 
  select(id)
```

